### 2014-04-15 paper/exampleobjects.tex
integrate gord comments, smash discussion sections into example  objects

@@

@@

@@

@@

@@

>>>>

Identification of these objects and gestures could also be performed using active acoustic sensing \cite{Ono-touchandactivate}: the internal pipes, although not externally visually distinctive, affect the acoustic signature of the object.  Intentional identity encoding using pipes could also be accomplished through print weight modification using fully enclosed pipes.

@@

Additional options for haptic feedback include the insertion of muscle wire into flexible printed pipes, creating shape changing interfaces \cite{Coelho-shapechanging}.

@@

Creating aural outputs using the printed pipes directly is also a possibility: the whistle in Figure \ref{fig:speculative}a is a fully printable audio output which is based on a Helmholz resonator, and which can be activated with air pressure.

@@

Some passive components required in the design of the recognition circuit could in the future be created using pipes and printed or injected conductive material.  For example, we printed a proof-of-concept  capacitor which features a thin printed plate with hollow cones on either side (see Figure \ref{fig:speculative}b).  After printing, we coated the inner surfaces of capacitor with copper paint.  It now can hold a charge of \valkyrie{xx}.  Similarly, tubes can be used to create \emph{resistors} in ``printed'' circuitry: a longer or thinner tube has a greater resistance than a shorter or wider one (see Figure \ref{fig:speculative}c).

@@

Integration of our maze with, e.g., PneUIs \cite{Yao-pneui} could result in a maze that helps a user along or blocks her path.

@@

A similar display could be created using colored liquids along with mixing and splitting topologies.  Mixing liquids in specific concentrations (e.g., for color output) could be performed using a servo-controlled gate as in Figure \ref{fig:direct}.

\begin{figure}
\centering
    \includegraphics[width=3.4in]{figures/speculative.png}
\caption{Some possible pipe uses.  The printed whistle in (a) is a Helmholz resonator: it creates a sound when air is blown through the pipe at the front, because air compresses at the small neck joint between the internal chamber and the pipe.  In (b), a capacitor manufactured on a 3D printer coated post-print with copper paint.  This particular one holds a charge of \valkyrie{XX}.  (c) gives a comparison of pipe-based resistors, also filled with copper paint.  For a cylindrical wire, resistance is based on its length and cross-sectional area.}
\label{fig:speculative}
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=3.4in]{figures/gates.png}
\caption{By attaching a servo to a gate structure, it is possible to direct fluid through that pipe.  The gate not only has binary positions (a) and (b), but can direct fractional flow, as well (c).}
\label{fig:direct}
\end{figure}

### 2014-04-15 paper/introduction.tex
need to merge
integrate gord comments, smash discussion sections into example  objects

\section{Introduction}
Makers, researchers, and professional designers (jointly ``makers" for the remainder of this paper) increasingly leverage 3D printers as tools for design work.  A wide array of objects, ranging from toy figurines to video game controllers and jet engine blades, are now prototyped (and sometimes even manufactured) using these machines.  Most models fabricated on 3D printers today are passive: they express the form, but not the function, of an object.

@@

Generating the appropriate pipes for these examples is not trivial.  For one, most 3D modelling tools do not provide extensive tools for modelling the  {\em interior} of 3D models. Furthermore, careful consideration needs to go into the design and routing of the pipes. Pipes need maximum possible bend radius to ease the insertion of media post-print.  Independent pipes cannot intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface: consumer-grade 3D printers do not guarantee air- or water-tightness of prints, so more than one printed layer may be required to prevent leakage.  Pipes for applications like illumunated EL wire signs must allow a single pipe to follow a specific path layout (e.g., for spelling out text).

>>>>

\section{Introduction}
Makers, researchers, and professional designers (jointly ``makers" for the remainder of this paper) increasingly leverage 3D printers as tools for design work.  A wide array of objects, ranging from toy figurines to video game controllers and jet engine blades, are now prototyped (and sometimes even manufactured) using these machines.  Most models fabricated on 3D printers today are passive: they express the form, but not the interactivity, of an object.

@@

Figure \ref{fig:teaser} shows a collection of interactive objects with various functionalities including haptic feedback, neon sign-like visual output, and selective touch-sensitivity.  All these objects have had the electronic components required to function redirected onto their surfaces using pipes.  But generating the appropriate pipes for these examples is not trivial.  For one, most 3D modelling tools do not provide extensive tools for modelling the  {\em interior} of 3D models. Furthermore, careful consideration needs to go into the design and routing of the pipes. Pipes need maximum possible bend radius to ease the insertion of media post-print.  Independent pipes cannot intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface: consumer-grade 3D printers do not guarantee air- or water-tightness of prints, so more than one printed layer may be required to prevent leakage.  Pipes for applications like illumunated EL wire signs must allow a single pipe to follow a specific path layout (e.g., for spelling out text).
